Fully Automatic Loop-free Program Synthesis by Bounded Model Checking

### 2013-10-11 paper/paper.tex
Mention sketch in experiments
Fix claim about linear scaling with word size

\subsection{Word Width: $w$}
An $\mathcal{L}$-program runs on a virtual machine (the $\mathcal{L}$-machine) that
has its own set of paramters.  The only relevant parameter is
the \emph{word width} of the $\mathcal{L}$-machine, that is, the number of bits
in each internal register and immediate constant.  This parameter is denoted by
$w$.  The size of the final SAT problem generated by {\sc cbmc} scales
approximately linearly with $w$, since each intermediate C variable corresponds
to $w$ propositional variables.

@@

>>>>

\subsection{Word Width: $w$}
An $\mathcal{L}$-program runs on a virtual machine (the $\mathcal{L}$-machine) that
has its own set of paramters.  The only relevant parameter is
the \emph{word width} of the $\mathcal{L}$-machine, that is, the number of bits
in each internal register and immediate constant.  This parameter is denoted by
$w$.  The size of the final SAT problem generated by {\sc cbmc} scales
polynomial with $w$, since each intermediate C variable corresponds
to $w$ propositional variables.

@@

We do not compare {\sc Kalashnikov} to {\sc Sketch}~\cite{sketch}, since the problem domains are
too different to make a meaningful comparison.
